Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectral calibration!

### 2014-04-26 tex/ms.tex
more intro words

Our example involves instantiating a ``calibration adjustment'' model,
which has a polynomial component and a non-parametric component.
The parameters of the calibration adjustment are nuisances, from a
scientific standpoint.
However, because the calibration adjustment is inferred along with the
parameters of interest, the probabilistic inference that provides
parameter estimates \emph{also} provides a spectrophotometric
calibration of the spectral data.
That is, the method we present has the potential to \emph{obviate
spectrophotometric calibration}.

>>>>

Our example involves instantiating a ``calibration adjustment'' model,
which itself has both a polynomial component and a non-parametric
component.
The parameters of the calibration adjustment are nuisances, from a
scientific standpoint.
However, because the calibration adjustment is inferred along with the
parameters of interest, the probabilistic inference that provides
parameter estimates \emph{also} provides a spectrophotometric
calibration of the spectral data.
That is, the method we present has the potential to \emph{obviate
spectrophotometric calibration}.
We find that this potential is realized.
